Implementation of a stable, high-power optical lattice for quantum gas microscopy

### 2018-01-31 LatticeOptics/latticeOpticsV4.tex
New RIN data Mephisto MOPA 55W, updated Fig3

Optical lattices holding an array of ultracold atoms have become a powerful experimental platform for a wide variety of investigations into various forms of quantum simulation \cite{Friedenauer2008, Kim2010, Struck2011, Simon2011, Yan2013, Drewes2016, Murmann2015}.%, strongly correlated systems, quantum state engineering, quantum computing and precision metrology.
Further, the recent advent of quantum gas microscopy~\cite{Bakr2009, Sherson2010, Haller2015, Cheuk2015, Parsons2015, Edge2015, Omran2015, Greif2016, Cheuk2016, Parsons2016, Boll2016, Cheuk2016a, Brown2016} has enabled studies that exhibit unprecedented control over few atom systems at extremely low energy scales, particularly those governed by the Hubbard Hamiltonian ~\cite{Hubbard1963}.
However, this progress has placed ever more stringent technical constraints on the lasers used to trap and manipulate the atomic systems.
For example, heating due to the intensity noise cannot be allowed to approach the longest thermalization timescales, lest the system fail to thermalize~\cite{Savard1997}.
Even if the system thermalizes, heating rates can limit the interrogation time available to probe a low-temperature state.
In a similar vein, experiments that rely on a small number of atoms held by multiple traps place stringent requirements on the relative positional stability of the traps, to ensure that the operations performed by the traps have adequate fidelity.%~\cite{Mazurenko2016}.FIXME: CITATIONS

@@

\begin{figure*}
  \begin{center}
    \includegraphics{fig/fig3_combined.pdf}
    \caption{\textbf{Laser noise of the lattice system.} (a) Shows the laser noise of unmodified Nufern fiber amplifiers and the Mephisto seed. (b) Shows the open (OL) and closed (CL) loop behavior of the high power feedback loop. (c) Shows open loop behavior of the low power feedback loop after making the modifications. (d) Closed loop behavior of the loop system without additional filtering, measured on the same setup as (c).}\label{fig:noises}
  \end{center}
\end{figure*}

>>>>

Optical lattices holding an array of ultracold atoms have become a powerful experimental platform for a wide variety of investigations into various forms of quantum simulation \cite{Friedenauer2008, Kim2010, Struck2011, Simon2011, Yan2013, Drewes2016, Murmann2015}. %, strongly correlated systems, quantum state engineering, quantum computing and precision metrology.
Further, the recent advent of quantum gas microscopy~\cite{Bakr2009, Sherson2010, Haller2015, Cheuk2015, Parsons2015, Edge2015, Omran2015, Greif2016, Cheuk2016, Parsons2016, Boll2016, Cheuk2016a, Brown2016} has enabled studies that exhibit unprecedented control over few atom systems at extremely low energy scales, particularly those governed by the Hubbard Hamiltonian ~\cite{Hubbard1963}.
However, this progress has placed ever more stringent technical constraints on the lasers used to trap and manipulate the atomic systems.
For example, heating due to the intensity noise cannot be allowed to approach the longest thermalization timescales, lest the system fail to thermalize~\cite{Savard1997}.
Even if the system thermalizes, heating rates can limit the interrogation time available to probe a low-temperature state.
In a similar vein, experiments that rely on a small number of atoms held by multiple traps place stringent requirements on the relative positional stability of the traps, to ensure that the operations performed by the traps have adequate fidelity.%~\cite{Mazurenko2016}.FIXME: CITATIONS

@@

\begin{figure*}
  \begin{center}
    \includegraphics{fig/fig3_combined.pdf}
    \caption{\textbf{Laser noise of the lattice system.} (a) Shows the laser noise of unmodified Nufern fiber amplifiers and the Mephisto seed, as well as an independent Mephisto MOPA 55W (not used for the optical lattice presented in this manuscript). (b) Shows the open (OL) and closed (CL) loop behavior of the high power feedback loop. (c) Shows open loop behavior of the low power feedback loop after making the modifications. (d) Closed loop behavior of the loop system without additional filtering, measured on the same setup as (c).}\label{fig:noises}
  \end{center}
\end{figure*}
